\begin{thebibliography}{9}

\bibitem{java-collections} Oracle Java Collections Framework Documentation,
\newblock \url{https://docs.oracle.com/javase/8/docs/technotes/guides/collections/},
\newblock Oracle Corporation, 2023.

\bibitem{data-structures} Cormen, T. H., Leiserson, C. E., Rivest, R. L., \& Stein, C.
\newblock \textit{Introduction to Algorithms, 3rd Edition},
\newblock MIT Press, 2009.

\bibitem{performance-analysis} Evans, B., \& Gough, J.
\newblock \textit{Java Performance: The Definitive Guide},
\newblock O'Reilly Media, 2014.

\bibitem{text-editors} Myers, E. W.
\newblock An O(ND) Difference Algorithm and its Variations,
\newblock \textit{Algorithmica}, 1(1-4), 251-266, 1986.

\bibitem{rope-data-structure} Boehm, H. J., Atkinson, R., \& Plass, M.
\newblock Ropes: An Alternative to Strings,
\newblock \textit{Software: Practice and Experience}, 25(12), 1315-1330, 1995.

\bibitem{concurrent-collections} Lea, D.
\newblock \textit{Concurrent Programming in Java: Design Principles and Patterns},
\newblock Addison-Wesley, 2000.

\bibitem{memory-management} Jones, R., \& Lins, R.
\newblock \textit{Garbage Collection: Algorithms for Automatic Dynamic Memory Management},
\newblock John Wiley \& Sons, 1996.

\bibitem{performance-optimization} Goetz, B.
\newblock \textit{Java Concurrency in Practice},
\newblock Addison-Wesley, 2006.

\bibitem{data-structure-survey} Sedgewick, R., \& Wayne, K.
\newblock \textit{Algorithms, 4th Edition},
\newblock Addison-Wesley, 2011.

\end{thebibliography} 